Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-13 analysis/paper/paper.Rmd
Fix typo, "Figure Figure"

There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).

>>>>

There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).
